Commutative Character Sheaves

### 2015-07-29 followup.tex
Types, under construction.
Added note to main definition.

Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
We will denote the category of character sheaves on $G$ by $\CS(G)$.

@@

Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$. Moreover, $C_0$ admits a smooth integral model $\underline{C}$

>>>>

Recall \cite{cunningham-roe:13a}*{Def. 1.1} that a character sheaf on $G$ is a triple $\cs{L} \ceq (\gcs{L}, \mu, \phi)$,
where $\gcs{L}$ is a rank-one $\ell$-adic local system on $\bG$, $\mu : \bm^* \gcs{L} \to \LxL$ is an isomorphism
of sheaves on $\bG \times \bG$, and $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an isomorphism of sheaves on $\bG$.
In \emph{loc. cit.}, $G$ was assumed to be commutative, but the same definition makes sense for non-commutative $G$.
We will denote the category of character sheaves on $G$ by $\CS(G)$.
\todo{I think we should hold the term `character sheaves for G', when $G$ is not commutative, in reserve, and not use it here for non-commutative $G$. So I might advocate going back to the full definition here.\\ -CC}

@@

Finally, consider the depth-zero supercuspidal representation $\pi_0$ of $\G^0(K)$.
Then $\pi_0$ is produced by compact induction from representation $\sigma$ of a compact mod centre subgroup $\underline{C}_0(\OK) \subset \G^0(K)$. Moreover, $C_0$ admits a smooth integral model $\underline{C}$ \todo{Under construction. \\ -CC}
